\documentclass{main}

\begin{document}

\section{Overview}
% What is anonymous communication
Anonymity describes situations where the acting person's identity is unknown.
The important idea here is that a person be non-identifiable, unreachable, or untrackable.
% Some small list of benefits of using anonymous communication
Anonymous online services allow people to communicate and share content without revealing their name or true identity.
The benefits of these tools include promoting free criticism, security to whistle blowers, prevention of individual data collection, privacy among individuals, etc.
%  Data is being collected from an individual including browsing history, online forms, and web
% searches that can be relatively innocent when examined in the context of that individual. Once this data is collected the consumer has no control over how this data is used, who has access to it, or how long the data exists. Online anonymity tools aim to mitigate this problem.
% Available tools
Nowadays, there are many tools being built for anonymous communications.
Onion routing and Garlic Routing are two of the most famous routing protocols for 
communicating anonymously on internet. These routing protocols route the data through
various nodes so that the path cannot be traced by someone looking the network.
VPN (Virtual Private Network)  also provide some level of anonymity but in VPNs,
user's privacy is in hands of a single person with access to the VPN servers.
There also exist remailers and rewebbers to provide anonymous e-mailing service(eg. ProtonMail)
and browsing services.

% Criminal Risk? --- Now or End of Report?


\end{document}